Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–-Moriya interactions in antiferromagnetic insulators

### 2019-02-06 Paper/paper.tex
style
more refs

In the prescence of an laser perturbation we can use the Peirls substitution to introduce the effect of the field trough the hopping amplitudes. We can write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively. According to the Peierls rule the hopping amplitudes gain a phase $e^{ie\bs{R}_{ij}\bs{A}(t)}$ where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$ and $\bs{A}$ is the vector potential $\bs{A}(t) = \frac{1}{2}(\vec{A}e^{-i\omega t} + \vec{A}^* e^{i\omega t})$, with $\vec{A} = \frac{iE_0}{\omega}\hat{e}$.

@@

\begin{figure}[t]
\includegraphics[width=0.6\columnwidth]{../Figures/NNvsNNN.pdf}
\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}}{J_{1,ij}^0}$ and $\tilde{D}_{2} = \frac{D_{2,ij}}{D_{2,ij}^0}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant. The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$. For $\tilde{J}_1$, similar results are obtained by Mentink et Al. \cite{Mentink2015}.}
\label{fig2}
\vspace*{-6pt}
\end{figure}

@@

%\begin{thebibliography}
\bibliography{paper}
%\end{thebibliography}

>>>>

\textit{Introducing laser perturbation}. In the prescence of an laser perturbation we can use the Peirls substitution to include the effect of the field trough the hopping amplitudes. We can write the electric field as $\bs{E}(t) = \frac{1}{2}(\vec{E}e^{-i\omega t}+\vec{E}^*e^{i\omega t})$, $\vec{E} = E_0\hat{e}$ and $\hat{e} = \frac{1}{\sqrt{1+\lambda_{POL}^2}}(\hat{e}_x+i\lambda_{POL}\hat{e}_y)$ is the polarization vector and $\lambda_{POL} = 0, \pm 1$ for plane polarized, right handed and left handed circular polarized field respectively. According to the Peierls rule the hopping amplitudes gain a phase $e^{ie\bs{R}_{ij}\bs{A}(t)}$ where $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$, $\bs{R}_i$ is the position of site $i$ and $\bs{A}$ is the vector potential $\bs{A}(t) = \frac{1}{2}(\vec{A}e^{-i\omega t} + \vec{A}^* e^{i\omega t})$, with $\vec{A} = \frac{iE_0}{\omega}\hat{e}$.

@@

\begin{figure}[t]
\includegraphics[width=0.6\columnwidth]{../Figures/NNvsNNN.pdf}
\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}}{J_{1,ij}^0}$ and $\tilde{D}_{2} = \frac{D_{2,ij}}{D_{2,ij}^0}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant. The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$. For $\tilde{J}_1$, similar results are obtained by Mentink et Al. \cite{Mentink2015}.}
\label{fig2}
\vspace*{-6pt}
\end{figure}
A similar Hamiltonian including a NN exchange term and a NNN DMI term was first proposed by S. A. Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}. Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}. This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.

@@

%\begin{thebibliography}
\bibliography{../MT}
%\end{thebibliography}
